Title Goes Here

### 2024-04-02 analysis/paper/paper.qmd
nice panel of basic things over time

ggplot(jobdata) +
  aes(year_ad_posted) +
  geom_bar() +
  scale_x_discrete(name = "Academic Year") +
  ylab("Number of tenure track job ads") +
  theme_minimal()

ggsave(here("analysis",
            "figures", 
            "fig-how-many-jobs-per-year.png"),
       height = 7,
       width = 22,
       bg ="white")
```

@@

# explore over time
jobdata %>%
  group_by(year_ad_posted) %>%
  count(job_title_simple) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot() +
  aes(year_ad_posted,
      prop,
      group = job_title_simple,
      colour = job_title_simple) +
  geom_line() +
  theme_minimal() +
  xlab("Year") +
  ylab("Proprtion of all tenure-track ads") +
  theme(legend.position = c(0.5, 0.5)) +
  guides(colour = guide_legend(nrow=2,
                               byrow=TRUE,
                               "Job title"))

ggsave(here("analysis",
            "figures", 
            "fig-prop-by-job-title-per-year.png"),
       bg ="white")

@@

# draw plot
  ggplot(count_of_tt_jobs_per_year_from_our_form) +
  aes(year, 
      group = 1,
      ratio_tt_2_ntt) +
  geom_line() +
  geom_hline(yintercept = 1,
             colour = "red") +
  annotate("text", 
           x = 3, 
           y = 1.1, 
           label = "1:1 ratio",
           colour = "red") +
  labs(y = "Ratio of tenure-track to non-tenure track\nand other jobs in Archaeology",
       x = "") +
  theme_bw(base_size = 14)

ggsave(here("analysis",
            "figures", 
            "fig-ratio-tt-2-ntt-jobs-per-year.png"),
       bg ="white")

>>>>

fig_how_many_jobs_per_year <- 
ggplot(jobdata) +
  aes(year_ad_posted) +
  geom_bar() +
  scale_x_discrete(name = "Academic Year") +
  ylab("Number of\ntenure track job ads") +
  theme_minimal(base_size = 14)

@@

# explore over time
fig_prop_by_job_title_per_year <- 
jobdata %>%
  group_by(year_ad_posted) %>%
  count(job_title_simple) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot() +
  aes(year_ad_posted,
      prop,
      group = job_title_simple,
      colour = job_title_simple) +
  geom_line(linewidth = 2) +
  theme_minimal(base_size = 14) +
  xlab("") +
  ylab("Proportion of\nall tenure-track ads") +
  theme(legend.position = c(0.5, 0.5)) +
  guides(colour = guide_legend(nrow=2,
                               byrow=TRUE,
                               "Job title")) +
   guides(x = "none")

@@

# draw plot
fig_ratio_tt_2_ntt_jobs_per_year <- 
  ggplot(count_of_tt_jobs_per_year_from_our_form) +
  aes(year, 
      group = 1,
      ratio_tt_2_ntt) +
  geom_line(linewidth = 2) +
  geom_hline(yintercept = 1,
             colour = "red") +
  annotate("text", 
           x = 3, 
           y = 1.3, 
           label = "1:1 ratio",
           colour = "red") +
  labs(y = "Ratio of tenure-track to\nnon-tenure track and other",
       x = "") +
  theme_minimal(base_size = 14) +
   guides(x = "none")

```{r}
# save these three plots as one set
library(cowplot)
plot_grid(
  fig_ratio_tt_2_ntt_jobs_per_year,
  fig_prop_by_job_title_per_year,
  fig_how_many_jobs_per_year,
  ncol = 1,
  align = "hv",
  axis = "lr"
)

ggsave(here("analysis",
            "figures", 
            "fig-panel-per-year.png"),
       bg ="white",
       h = 11, # experiment with h and w to get the right size and proportion 
       w = 20,
       units = "in",
       dpi = 900) # make the image nice and crisp
